|

### 2023-05-09 manuscript/Chapter2-appendix1.Rmd
remove line in appendix1

# plogis for the success parameters
# Take the exponent of sigma parameters
b_draws[
  , c("b_successnovice_Intercept",
      "b_successinterm_Intercept",
      "b_successadvanced_Intercept",
      "b_successnovice_sqrt_game_duration",
      "b_successinterm_sqrt_game_duration",
      "b_successadvanced_sqrt_game_duration"
  )
  := lapply(.SD, function(x) {plogis(x)}),
  .SDcols = c(
    "b_successnovice_Intercept",
    "b_successinterm_Intercept",
    "b_successadvanced_Intercept",
    "b_successnovice_sqrt_game_duration",
    "b_successinterm_sqrt_game_duration",
    "b_successadvanced_sqrt_game_duration"
  )
]

>>>>

# plogis for the success parameters
b_draws[
  , c("b_successnovice_Intercept",
      "b_successinterm_Intercept",
      "b_successadvanced_Intercept",
      "b_successnovice_sqrt_game_duration",
      "b_successinterm_sqrt_game_duration",
      "b_successadvanced_sqrt_game_duration"
  )
  := lapply(.SD, function(x) {plogis(x)}),
  .SDcols = c(
    "b_successnovice_Intercept",
    "b_successinterm_Intercept",
    "b_successadvanced_Intercept",
    "b_successnovice_sqrt_game_duration",
    "b_successinterm_sqrt_game_duration",
    "b_successadvanced_sqrt_game_duration"
  )
]
